Reconstructing the Lensing Mass in the Universe \\ from Photometric Catalogue Data

### 2013-03-02 doc/paper-lcr.tex
Edited section 8, added thoughts, made setup clearer?

\section{Systematic Errors due to using an incorrect Stellar Mass--Halo Mass Relation}
\label{sec:SHAMfail}

@@

\new{
Throughout this work we have assumed that the universe's halos are populated with galaxies whose stellar masses are determined purely by the \citet{BehrooziEtal2010} Stellar Mass--Halo Mass relation. The real universe is unlikely to follow this relation perfectly; the result is that an ensemble of real lines of sight will differ from the ensemble of calibration lines of sight, potentially introducing a systematic error to the reconstructed convergence.

We test the potential size of this systematic error by using the \citet{BehrooziEtal2010} relation to generate the stellar masses of our calibration lines of sight, but the stellar mass--halo mass relation of \citet{MosterEtal2010} for the ``real'' lines of sight that are reconstructed.

For halos masses of $\sim 10^{12} \Msun$ both stellar mass--halo mass relations estimate a stellar mass of $\sim 10^{10.5} \Msun$, but for halos more massive that this the stellar masses generated from the Moster relation are systematically higher than those generated from the Behroozi relation. At halo masses of $\sim 10^{14} \Msun$ the best fit stellar masses differ by $\sim 0.25$ dex.

Applying our Behroozi--based reconstruction to lines of sight with Moster stellar masses results in systematically overestimating $\kappax$. In \Fref{fig:SHAMbias} we show the resulting bias on the inferred $\kappax$ after combining several lines of sight. With a purely photometric reconstruction there is a typical systematic bias of $\sim 0.025$ on the reconstructed convergence, although it can be shrunk to $\sim 0.01$ if only the low $\kappax$ lines of sight are used, however for the high shear lines of sight the bias is $\sim 0.04$. It is not suprising that the low $\kappax$ lines of sight are least affected by changes in the stellar mass--halo mass relation. Low $\kappax$ lines of sight are relatively empty hence their $\kappah$ values are small and do not change significantly with stellar mass--halo mass relation. The high shear lines of sight have significantly overestimated $\kappax$ since they tend to lie close to massive halos. This is the regime where the Moster and Behroozi relations are most different. Interestingly overestimating the $\kappah$ values of high shear lines of sight pushes them into the region where the $\kappah$ to $\kappax$ calibration is least certain; this has significantly decreased the precision of the reconstructed $\kappax$.

Despite the systematic errors the photometric reconstruction is still sufficient to choose the best lines of sight for spectroscopic follow-up. With targetted spectroscopy the systematic error decreases to $\sim 0.014$ for the ensemble, $\sim 0.005$ for the low kappa sample and $\sim 0.018$ for the high shear sample. This result provides further motivation for prioritizing the lenses that reside on the underdense lines of sight.

The systematic errors reported herein may be overly pessimistic; the bias is due to differences in the stellar masses predicted for high mass halos. If observations can discriminate between the high mass end of the \citet{BehrooziEtal2010} and \citet{MosterEtal2010} relations then the systematic error on the reconstruction will decrease.
}

>>>>

\section{Systematic Errors due to Assuming an Incorrect 
Stellar Mass--Halo Mass Relation}
\label{sec:SHAMfail}

@@

\new{
Throughout this work we have assumed that the universe's halos are populated
with galaxies whose stellar masses are determined purely by the
\citet{BehrooziEtal2010} Stellar Mass--Halo Mass relation, which we then use
in our reconstruction. In practice, the true Stellar Mass--Halo Mass relation
may well be different to the one we assume in our inference, and if it is, 
a systematic error could be incurred.

We investigate the potential size of this systematic error by repeating the
analysis of the previous section, still using the  the
\citet{BehrooziEtal2010} relation to generate the stellar masses of our
calibration lines of sight and hence carry out the inference, but now using
simulated catalog datasets that were generated from the stellar mass--halo
mass relation of \citet{MosterEtal2010}.

This relation provides a comparable fit to the stellar mass function to the
Behroozi et al relation, so represents a plausible alternative to our assumed
form. For halo masses of $\sim 10^{12} \Msun$, both stellar mass--halo mass
relations predict a stellar mass of $\sim 10^{10.5} \Msun$, but for halos more
massive than this the stellar masses generated from the Moster relation are
systematically higher than those generated from the Behroozi relation. At halo
masses of $\sim 10^{14} \Msun$ the predicted stellar masses differ by some 
$0.25$ dex.

Applying our Behroozi--based reconstruction to lines of sight with Moster
stellar masses results in systematic overestimates of $\kappax$. In
\Fref{fig:SHAMbias} we show this bias emerging after combining several lines
of sight. With a purely photometric reconstruction there is a typical
systematic bias of $\sim 0.025$ on the reconstructed convergence. This can be
shrunk to $\sim 0.01$ if only the low $\kappax$ lines of sight are used;
however for the high shear lines of sight the bias is $\sim 0.04$. It is not
too suprising that the low $\kappax$ lines of sight are least affected by
changes in the stellar mass--halo mass relation. Low $\kappax$ lines of sight
are relatively empty, their $\kappah$ values are small, and they do not depend
as strongly on the stellar mass--halo mass relation. In contrast, the high
shear lines of sight have significantly overestimated $\kappax$ values, since
they tend to lie close to massive halos -- the regime where the Moster
and Behroozi relations are most different. Interestingly, overestimating the
$\kappah$ values of high shear lines of sight pushes them into the region
where the $\kappah$ to $\kappax$ calibration is least certain; this 
significantly decreases the precision of the reconstructed $\kappax$.

Despite these systematic errors, we find that the photometric reconstruction
is still sufficient to choose the best lines of sight for spectroscopic
follow-up. With targeted spectroscopy the systematic error decreases to $\sim
0.014$ for the ensemble, $\sim 0.005$ for the low kappa sample and $\sim
0.018$ for the high shear sample. These results provides further motivation for
prioritizing the lenses that reside on the underdense lines of sight.

The systematic errors reported here are perhaps overly pessimistic, because
the bias is due to differences in the stellar masses predicted for high mass
halos. If new observations can discriminate between the high mass end of the
\citet{BehrooziEtal2010} and \citet{MosterEtal2010} relations, then the
systematic error on the reconstruction will decrease. Similarly, incorporating
additional information about the high mass group and cluster-scale halo
systems, such as their richness or other occupation statistics, would help
mitigate the stellar to halo mass conversion error. }
